%Author: Christopher Sara
% 
%
%
%Copyright 2014 



\documentclass[12pt]{article}
%a4paper,
%twoside,


% encoding, font, language
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage{lmodern}
\usepackage[ngerman, english]{babel}
\usepackage{gensymb}
\usepackage{nicefrac}
\usepackage{titlesec}

\usepackage[
    handwritten,
    nowarnings,
    %myconfig
]{xcookybooky}

\usepackage{blindtext}    % only needed for generating test text

\definecolor{mygreen}{rgb}{0,.5,0}
\DeclareRobustCommand{\textdegree}{\ensuremath{^{\circ}\mathrm{F}}}

\renewcommand{\familydefault}{\sfdefault}


%----------------------------------------------------------------------------------------
%	SET RECIPE COLORS
%----------------------------------------------------------------------------------------
\setRecipeColors
{%
    recipename = mygreen,
    ing = blue,
    inghead = blue,
    prep,
    prephead,
    hint,
    hinthead,
}


%----------------------------------------------------------------------------------------
%	SET RECIPE HEADLINE NAMES
%----------------------------------------------------------------------------------------


\setHeadlines{
inghead = Ingredients,
prephead = Directions,
preparationtime = Preparation,
bakingtime = Cook,
hinthead = Hint,
calory = Calories, % deal w/ it the dude that wrote this is german
portion = Servings,
portionvalue =,
continuationhead = Continuation,
continuationfoot = Continuation on next page,
source = By
}

%----------------------------------------------------------------------------------------
%	SECTION OPTIONS
%----------------------------------------------------------------------------------------

\setcounter{secnumdepth}{1}

\renewcommand*{\recipesection}[2][]
{%
    \subsubsection[#1]{#2}
}
\renewcommand{\subsectionmark}[1]
{% no implementation to display the section name instead
}


%%%%%%%%%%
% hyperref
\usepackage{hyperref}    % must be the last package
\hypersetup{%
    pdfauthor            = {Christopher Sara},
    pdftitle             = {Cookbook!},
    pdfsubject           = {Recipes},
    pdfkeywords          = {recipes},
    pdfstartview         = {FitV},             
    pdfview              = {FitH},
    pdfpagemode          = {UseNone}, % Options; UseNone, UseOutlines
    bookmarksopen        = {true},
    pdfpagetransition    = {Glitter},
    colorlinks           = {true},
    linkcolor            = {black}, 
    urlcolor             = {black}
    citecolor            = {black}, 
    filecolor            = {black},
}
% hyperref
%%%%%%%%%%



\begin{document}

\title{Cookbook v0.1}
\author{Christopher Sara}
\maketitle

\newpage

\tableofcontents

%\vspace{9em}

\newpage

\section{Breakfast}
\newpage

\begin{recipe}
[ % 
    preparationtime = {\unit[30]{min}},
    bakingtime={\unit[45]{min}},
    bakingtemperature={\protect\bakingtemperature{fanoven=\unit[350]{\textdegree}F}},
    %bakingtemperature={\protect\bakingtemperature{fanoven=\unit[230]{\textdegree}F, topbottomheat=\unit[195]{\textdegree}F, topheat=\unit[195]{\textdegree}F, gasstove=Stove 2}},
    portion = {\portion{4--5}},
    source = Jennifer Sara
]
{Egg Casserole}
    
    %\graph
    %{% pictures
       % small=pic/glass,     % small picture
        %big=pic/ingredients  % big picture
    %}
    
    \ingredients
    {%
    	1 & lb.  & breakfast sausage \\
    	6--8 &   & eggs \\
    	2 & c  & milk \\
        1 & tsp & dry mustard\\
        4--5 & slices & cubed white bread \\
        1 & c & cheese\\
        1 & tsp & salt\\               
    }
    
    \preparation
    {%
    	\step Brown sausage in a pan and drain fat.
        \step Beat eggs in a large bowl. 
        \step Add milk, mustard, and bread. Stir.
        \step Add the cheese and sausage.
        \step Place mixture into a greased 13x9 pan.
        \step Preheat oven to \unit[350]{\textdegree}F. Bake for 45 minutes. 
    }
    
    \hint{Substitute the sausage for your preferred vegetables or use both.}
\end{recipe}
\newpage

\section{Dinner}
\begin{recipe}
[ % 
    preparationtime = {\unit[10]{min}},
    bakingtime={\unit[20-25]{min}},
   % bakingtemperature={\protect\bakingtemperature{fanoven=\unit[300]{\textdegree}F}},
    %bakingtemperature={\protect\bakingtemperature{fanoven=\unit[230]{\textdegree}F, topbottomheat=\unit[195]{\textdegree}F, topheat=\unit[195]{\textdegree}F, gasstove=Stove 2}},
    portion = {\portion{5-6 Servings}},
    source = Jennifer Sara
]
{Chicken Wings \& Rice}
    
    %\graph
    %{% pictures
       % small=pic/glass,     % small picture
        %big=pic/ingredients  % big picture
    %}
    
    \ingredients
    {%
    	\
        2 & pckgs & wings\\
	$3 \nicefrac{1}{2}$ & c  & chicken broth \\
	$1 \nicefrac{1}{2}$ & c  & white rice, uncooked \\
	$\nicefrac{3}{4}$ & c  & flour \\
	$\nicefrac{1}{2}$ & c  & white rice, uncooked \\
	$\nicefrac{1}{2}$ & tsp.  & salt \\
	$\nicefrac{1}{2}$ & tsp. & pepper \\
	$\nicefrac{1}{2}$ & tsp. & thyme\\
	$\nicefrac{1}{2}$ & cbe  & butter \\
        2 & stalks & celery\\
        2 & & green onions, sliced\\              
    }
    
    \preparation
    {%
    	\step Wash chicken and dry with paper towel.
        \step Combine flour, salt, pepper, and thyme in a paper or Ziplc bag.
        \step Add chicken and coat with mixture.
        \step Melt butter in skillet over medium-high heat.
        \step Shake off excess coating from chicken and brown with butter until browned and cooked.
        \step Remove chicken to plate and keep warm.
        \step Add celery, onion, and rice. Stir until brown.
        \step Add broth and return chicken and accumulated juiced to skillet.
        \step Cover tightly and simmer with lid on for 20-25 minutes until rice is cooked. Stir occasionally.
    }
    
    \hint{Can be served with toasted almond on top and/or cranberry sauce}

\end{recipe}
\newpage

\begin{recipe}
[ % 
    preparationtime = {\unit[15]{min}},
    bakingtime={\unit[20]{min}},
   bakingtemperature={\protect\bakingtemperature{fanoven=\unit[375]{\textdegree}F}},
    %bakingtemperature={\protect\bakingtemperature{fanoven=\unit[230]{\textdegree}F, topbottomheat=\unit[195]{\textdegree}F, topheat=\unit[195]{\textdegree}F, gasstove=Stove 2}},
    portion = {\portion{5-6 Servings}},
    source = Christopher Sara
]
{Chow Fun}
    
    %\graph
    %{% pictures
       % small=pic/glass,     % small picture
        %big=pic/ingredients  % big picture
    %}
    
    \ingredients
    {%    	
        8  & oz.  & flank steak \\
    	 $1 \nicefrac{1}{2}$ & tsp  & corn starch \\
    	 2 & tsp  & dark soy sauce \\
        1 & tsp & sesame oil\\ 
        1 & lb & fresh rice noodles (~half inch width)\\              
        3 &  & green onions\\
        2 & tsp & minced garlic\\
        2 & tsp & minced ginger\\
        $\nicefrac{1}{4}$ & tsp  & white pepper \\
        $\nicefrac{1}{2}$ & tsp  & sugar \\
        $1 \nicefrac{1}{2}$ &   & soy sauce \\
        1 & tbls  & Shaoxing rice wine \\ 
	  2 & tbls & oyster sauce\\
	  2 & tbls & water \\
	  1 & tbls & fermented black beans (mashed)\\
	  3 & cups & bean sprouts (rinsed)\\
	  3 & tbls & canola oil\\                    
    }
    
    \preparation
    {%
    	\step Cut beef into 2-inch wide strips. Cut those strips into $\nicefrac{1}{4}$ 
    	\step Transfer beef into a bowl and add cornstarch, dark soy sauce, and sesame oil. Stir and massage meat then set aside.    
    	\step Separate noodles into strips. Set aside on a plate.
    	\step Cut up green onion and add it into a small bowl with the garlic and ginger.
    	\step In another bowl, stir together sugar, white pepper, soy sauce, rice wine, oyster sauce, and water.
    	\step In a wok or large skillet, swirl in 1 tbls of oil and add the ginger/garlic mix. Stir fry for about 15 seconds then set on the side. 
    	\step Add the beef and spread it out in a flat layer. Sear for 1 minute undisturbed then add the black beans. Stir fry for 30 seconds. Transfer to a clean plate.
    	\step Swirl in the remaining 2 tbls of oil, then add the noodles. Sear for 1 minute undisturbed until crusty. Dump the bean sprouts and stir fry for about 1 minute. 
    	\step Return the beef and juices and stir to combine. Stir fry for around another minute to finish cooking the beef.
    	\step Pile onto a platter and serve immediately. 
    }
    
    \hint{Cut up a bit of onion or add some chili paste for an extra kick!}

\end{recipe}
\newpage 
\begin{recipe}
[ % 
    preparationtime = {\unit[15]{min}},
    bakingtime={\unit[20]{min}},
   bakingtemperature={\protect\bakingtemperature{fanoven=\unit[375]{\textdegree}F}},
    %bakingtemperature={\protect\bakingtemperature{fanoven=\unit[230]{\textdegree}F, topbottomheat=\unit[195]{\textdegree}F, topheat=\unit[195]{\textdegree}F, gasstove=Stove 2}},
    portion = {\portion{5-6 Servings}},
    source = Christopher Sara
]
{Garlic Shrimp Rigatoni}
    
    %\graph
    %{% pictures
       % small=pic/glass,     % small picture
        %big=pic/ingredients  % big picture
    %}
    
    \ingredients
    {%    	
        1  & lb.  & raw shrimp (tail-off) \\
    	4 & cloves  & garlic \\
    	1 & tbls  & butter \\
        6 & oz & Rigatoni\\ 
        1 & can & fire-roasted tomatoes\\              
        16 & oz & alfredo\\
        $\nicefrac{1}{4}$ & cup  & Parmesan cheese \\         
    }
    
    \preparation
    {%
    	\step Preheat oven to 375 {\textdegree}F.  
    	\step Cook pasta in a pot.      
    	\step In a skillet, melt 1 tablespoon of butter and saut\'{e} garlic.  Add shrimp and cook. Set aside.
    	\step Drain pasta and add to baking pan. 
    	\step Add tomatoes, alfredo, and cooked shrimp to the pan. Top with Parmesan if desired. 
    	\step Put in oven for about 10-15 minutes or until cheese is golden brown on top.
    }
    
    \hint{A 13x9 fits this dish perfectly.}

\end{recipe}
\newpage 

\begin{recipe}
[ % 
    preparationtime = {\unit[20]{min}},
    bakingtime={\unit[30]{min}},
   bakingtemperature={\protect\bakingtemperature{fanoven=\unit[350]{\textdegree}F}},
    %bakingtemperature={\protect\bakingtemperature{fanoven=\unit[230]{\textdegree}F, topbottomheat=\unit[195]{\textdegree}F, topheat=\unit[195]{\textdegree}F, gasstove=Stove 2}},
    portion = {\portion{4 Servings}}
]
{Stuffed Bell Peppers}
    
    %\graph
    %{% pictures
       % small=pic/glass,     % small picture
        %big=pic/ingredients  % big picture
    %}
    
    \ingredients
    {%
    	\
        4 &  & bell peppers (tops removed, seeded)\\
	 1 & lb.  & ground meat \\
	 1  &   & bell pepper (chopped) \\
	 1  & c  & spinach  \\
	 1  & 14oz  can  & diced tomatoes \\
	 1 & c  & slisced mushrooms \\	
	 1 &  & zucchini (chopped)\\
	    &  & garlic powder\\
          &  & Italian seasoning\\
          &  & salt/pepper      \\        
    }
    
    \preparation
    {%
    	 \step Preheat oven to 350 {\textdegree}F.
        \step Wrap 4 bell peppers in aluminum foil and place in a baking dish. Bake for 15 minutes in the preheated oven then remove from heat.
        \step In a skillet over medium heat, cook the meat until browned. Set Aside.
        \step Heat oil in skillet and cook onion, spinach, mushrooms, zucchini, and chopped bell pepper until tender. 
        \step Return meat to skillet.
        \step Mix in tomatoes and tomato paste. Season with Italian seasoning, garlic powder, salt, and pepper. 
        \step Stuff peppers with the skillet mixture.
        \step Return peppers to oven and bake for 15 minutes.
    }
    
    %\hint{Can be served with toasted almond on top and/or cranberry sauce}

\end{recipe}
\newpage

\section{Salads}
\newpage
\section{Sauces}
\newpage

\begin{recipe}
[ % 
    preparationtime = {\unit[15]{min}},
    bakingtime={\unit[20]{min}},
   bakingtemperature={\protect\bakingtemperature{gasstove=Low}},
    %bakingtemperature={\protect\bakingtemperature{fanoven=\unit[230]{\textdegree}F, topbottomheat=\unit[195]{\textdegree}F, topheat=\unit[195]{\textdegree}F, gasstove=Stove 2}},
    portion = {\portion{5-6 Servings}},
    source = Christopher Sara
]
{Marinara Sauce}
    
    %\graph
    %{% pictures
       % small=pic/glass,     % small picture
        %big=pic/ingredients  % big picture
    %}
    
    \ingredients
    {%    	
        5-6  & cloves  & garlic \\
    	 3-2  &   & tomatoes \\
    	 48 & oz & crushed tomatoes\\
        1 & can & tomato paste\\ 
        $\nicefrac{1}{2}$ & tsp. & red pepper flakes\\              
        2 & tsp & Italian seasoning\\
        2-3 & tbls  & extra virgin olive oil \\         
    }
    
    \preparation
    {%
    	\step Crush tomatoes 
    	\step Cut up tomatoes.
    	\step Saut\'{e} garlic in olive oil with red pepper flakes and Italian seasoning.  
    	\step Add tomatoes until soft then take off the heat.
    	\step Put saut\'{e} in a Crockpot. Add the crushed tomatoes and tomato paste.
    	\step Cook on low for 5-6 hours. Stir occasionally.
    }
    
    \hint{Contadina crushed tomatoes are a good canned tomato. Also, add more red pepper flakes for a spicier sauce.}

\end{recipe}
\newpage 
\section{Desserts}
\begin{recipe}
[ % 
    preparationtime = {\unit[1]{h}},
    bakingtime={\unit[1]{h}},
    bakingtemperature={\protect\bakingtemperature{fanoven=\unit[300]{\textdegree}F}},
    %bakingtemperature={\protect\bakingtemperature{fanoven=\unit[230]{\textdegree}F, topbottomheat=\unit[195]{\textdegree}F, topheat=\unit[195]{\textdegree}F, gasstove=Stove 2}},
    portion = {\portion{10-12 Slices}},
    source = Jennifer Sara
]
{Banana Bread}
    
    %\graph
    %{% pictures
       % small=pic/glass,     % small picture
        %big=pic/ingredients  % big picture
    %}
    
    \ingredients
    {%
    	$\nicefrac{1}{2}$ & c  & butter (room temp.) \\
    	$\nicefrac{1}{2}$ & c  & sugar \\
    	$\nicefrac{1}{2}$ & c  & brown sugar \\
        1 & tsp & vanilla\\
        2 & & eggs \\
        2 & c & flour\\
        1 & tsp & baking soda\\ 
        2 & overripe & bananas \\
	$\nicefrac{1}{2}$ & c & walnuts and/or \\ & chocolate chips \\               
    }
    
    \preparation
    {%
    	\step Preheat oven to 300 {\textdegree}F.
        \step Mix butter, sugar, and vanilla into a medium sized bowl. 
        \step While stirring, add in one egg at a time.
        \step Add baking soda.
        \step Stir in flour $\nicefrac{1}{2}$ c at a time until completely mixed in.
        \step You may add in $\nicefrac{1}{2}$ c and/or $\nicefrac{1}{2}$ c chocolate chips if you like.
        \step Place dough in well-greased or non-stick bread pan. Smooth the top.
        \step Put in oven for 65--70 minutes.  Test near the end to make sure dough has fully baked.
        \step Let bread cool in the pan for 10 minutes then put the bread on a rack to cool.        
    }
    
    \hint{Be sure to allow bread cool well before slicing.}

\end{recipe}

\begin{recipe}
[ % 
    preparationtime = {\unit[10]{min}},
    bakingtime={\unit[30]{min}},
    bakingtemperature={\protect\bakingtemperature{fanoven=\unit[325]{\textdegree}F}},
    %bakingtemperature={\protect\bakingtemperature{fanoven=\unit[230]{\textdegree}F, topbottomheat=\unit[195]{\textdegree}F, topheat=\unit[195]{\textdegree}F, gasstove=Stove 2}},
    portion = {\portion{12 bars}},
    source = Jennifer Sara
]
{Cookie Dough Cheesecake Bars}
    
    %\graph
    %{% pictures
       % small=pic/glass,     % small picture
        %big=pic/ingredients  % big picture
    %}
    
    \ingredients
    {%
    	%$\nicefrac{1}{2}$ & c  & butter (room temp.) \\
    	%$\nicefrac{1}{2}$ & c  & sugar \\
    	%$\nicefrac{1}{2}$ & c  & brown sugar \\
        % 1 & tsp & vanilla\\             
    }
    
    \preparation
    {%
    	\step Preheat oven to 325 {\textdegree}F.       
    }
    
    \hint{Be sure to allow bread cool well before slicing.}

\end{recipe}
\newpage

\begin{recipe}
[ % 
    preparationtime = {\unit[10]{min}},
    bakingtime={\unit[30]{min}},
    bakingtemperature={\protect\bakingtemperature{fanoven=\unit[350]{\textdegree}F}},
    %bakingtemperature={\protect\bakingtemperature{fanoven=\unit[230]{\textdegree}F, topbottomheat=\unit[195]{\textdegree}F, topheat=\unit[195]{\textdegree}F, gasstove=Stove 2}},
    portion = {\portion{One 13x9}},
]
{Snickerdoodle Bars}
    
    %\graph
    %{% pictures
       % small=pic/glass,     % small picture
        %big=pic/ingredients  % big picture
    %}
    
    \ingredients
    {%
    	$2 \nicefrac{2}{3}$ & c  & all-purpose flour \\
        2 & c & dark brown sugar\\
        1 & c & \textbf{unsalted} butter, room temp. \\
        2 &  & eggs\\
        3 & tbls & white sugar\\ 
        1 & tbls & Vanilla \\
	3 & tsps & groud cinnamon \\
	2 & tsps & baking powder \\
	1 & tsps & salt \\                
    }
    
    \preparation
    {%
    	\step Preheat oven to 350 {\textdegree}F. Lightly grease a 13x9 baking pan.
        \step In a medium bowl, whisk together the flour, baking powder, and salt.  
        \step In a large mixing bowl, beat together the butter, brown sugar, eggs, and vanilla until smooth. 
        \step Add the flour mixture to the egg mixture and beat until well blended.
        \step Spread the batter evenly in the prepared pan with a spoon or rubber scraper.
        \step In a small bowl, combine the white sugar and cinnamon. 
        \step Sprinkle the mixture evenly over the batter in the baking pan. Spread around top of batter.
        \step Bake for 25-30 minutes or until the surface springs back when gently pressed. 
        \step Remove from oven and let cool it slightly on a wire rack.   
    }
    
    \hint{If you use salted butter, you're gonna have a bad time.}

\end{recipe}

\end{document}